%-------------------------
% Data Engineer Resume
% Author : Cody Hou
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{12pt}  % or any value you prefer, like 15pt
\usepackage[T1]{fontenc}
\input{glyphtounicode}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage{xcolor} 
\definecolor{UQPurple}{RGB}{115, 41, 130}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{UQPurple}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{UQPurple}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  {\Huge \scshape Cody Hou} \\ \vspace{5pt}
  \small \raisebox{-0.1\height}\faPhone\ +61 478813670~ 
  \href{mailto:cody.houx@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{cody.houx@gmail.com}} ~
  \faMapMarker\ Brisbane, QLD, Australia ~
  \href{https://www.linkedin.com/in/ce-hou}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
  \href{https://github.com/DataCody}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
  \href{https://datacody.github.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
  \vspace{-8pt}
\end{center}

%-----------------Summary----------------

\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={•}]
\setlength{\itemsep}{-3pt}
    \item \textbf{Data Analyst} with proven expertise in building \textbf{scalable ETL/ELT pipelines}, cloud-based data architectures, and high-performance analytics platforms across energy, finance, and public health sectors.
    \item Experienced in \textbf{SQL, Python, dbt, Spark, and Databricks}, with strong proficiency in \textbf{Snowflake, BigQuery, and Redshift} for data modeling, transformation, and performance optimization.
    \item Skilled in designing \textbf{data workflows and orchestration} using Airflow and Dagster, ensuring reliability, automation, and compliance across enterprise and government environments.
    \item Passionate about leveraging \textbf{cloud platforms (AWS, GCP, Azure)} and modern DevOps practices (Docker, Kubernetes, GitHub Actions, GitLab CI/CD) to enable \textbf{scalable, secure, and production-ready data infrastructure}.
\end{itemize}
\vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\setlength{\itemsep}{-3pt}
\item \textbf{Languages:} Python, SQL, R, Bash.
\item \textbf{Data Storage:} BigQuery, Databricks, Redshift, Snowflake.
\item \textbf{ETL \& ELT:} dbt, Fivetran, Spark.
\item \textbf{Workflow Orchestration:} Airflow, Dagster.
\item \textbf{Cloud Platforms:} AWS, Azure, GCP.
\item \textbf{Containerization:} Docker, Kubernetes.
\item \textbf{Data Visualization:} Power BI, Tableau.
\item \textbf{Version Control \& CI/CD:} Git, GitHub Actions, GitLab CI/CD.
\end{itemize}
\vspace{-18pt}

% -----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Data Analyst}{Jun 2025 -- Aug 2025}
{Renox Technologies}{Full-Time}
\resumeItemListStart
\resumeItem{Built end-to-end \textbf{ETL} pipelines integrating data from \textbf{AWS Redshift}, SCADA systems, and RESTful APIs into centralized reporting platforms, enabling automated KPI tracking and advanced analytics.}
\resumeItem{Designed and automated Python-based data workflows to simulate PV + battery systems, validating results against actual site performance to calculate and benchmark Performance Ratio (PR), with full \textbf{version control} and \textbf{CI/CD} automation managed in \textbf{GitLab}.}
\resumeItem{Developed and maintained reports and dashboards, delivering data-driven insights on energy storage solutions, cost savings, and ROI to support customer decision-making.}
\resumeItem{\textbf{Key Achievements}: 
\vspace{-4pt}
    \begin{itemize}
        \item Helped clients achieve \textbf{Net-Zero energy costs}, reducing annual electricity expenditure from \textbf{AUD 1.03M} to \textbf{Bill Zero}.
        \item Delivered ROI in just \textbf{4 years}, supported by data-driven PV + battery system design and cost-benefit analysis.
    \end{itemize}
}
\resumeItemListEnd

\resumeSubheading
{Analytics Engineer}{Mar 2025 -- Present}
{Upwork}{Remote}
\resumeItemListStart
\resumeItem{Engineered and deployed cloud-based data pipelines using \textbf{dbt}, \textbf{Google BigQuery}, \textbf{Snowflake}, and \textbf{Databricks}, with \textbf{GitHub Actions} for CI/CD, transforming raw transactional data into structured analytics models to enable actionable insights for clients.}
\resumeItem{Implemented robust data transformation workflows to clean, join, and aggregate datasets across multiple cloud platforms, improving reporting efficiency, data accessibility, and scalability.}
\resumeItem{Developed and executed automated data tests and documentation practices to ensure data integrity, reliability, and model transparency.}
\resumeItem{\textbf{Key Achievements}: 
\vspace{-4pt}
    \begin{itemize}
        \item Successfully transformed and modeled over 1 million rows of transactional data across multiple platforms, improving reporting efficiency and data accessibility.
        \item Reduced manual data processing time by 40\% through automation and streamlined multi-cloud workflows.
        \item Enhanced data quality and reliability by implementing comprehensive testing, validation, and documentation procedures.
    \end{itemize}
}
\resumeItemListEnd

\resumeSubheading
{Data Consultant}{Dec 2024 -- Feb 2025}
{Centauri Alpha}{Remote}
\resumeItemListStart
\resumeItem{Designed and implemented custom analytics solutions using \textbf{BigQuery}, \textbf{dbt}, \textbf{Power BI}, and \textbf{Python} to help small businesses optimize decision-making.}
\resumeItem{Developed predictive models and interactive dashboards, leveraging \textbf{dbt} for data transformations and \textbf{BigQuery} for scalable data warehousing.}
\resumeItem{Automated \textbf{ETL/ELT workflows}, improving data processing speed, data quality, and reproducibility.}
\resumeItem{Collaborated with marketing and finance teams to define \textbf{KPIs} and deliver dashboards that supported strategic business growth.}
\resumeItem{Analyzed complex, multi-dimensional datasets to generate actionable insights for client acquisition and retention strategies.}
\resumeItem{\textbf{Key Achievements}: 
\vspace{-4pt}
    \begin{itemize}
        \item Optimized KPI dashboards, leading to a 20\% \textbf{improvement} in business goal alignment.  
        \item Enhanced customer acquisition strategies, resulting in a 25\% \textbf{increase} in client growth.  
    \end{itemize}
}
\resumeItemListEnd

\resumeSubheading
{Research Assistant - Data Analyst}{Jun 2024 -- Oct 2024}
{The University of Queensland}{Brisbane}
\resumeItemListStart
\resumeItem{Collected, cleaned, and analyzed \textbf{infectious disease} data from diverse sources to provide actionable insights.}
\resumeItem{Identified trends, patterns, and correlations in large, multi-dimensional datasets, driving \textbf{data-driven} decision-making.}
\resumeItem{Created impactful \textbf{reports} and \textbf{presentations}, clearly communicating key findings and recommendations to \textbf{stakeholders}.}
\resumeItem{Collaborated closely with stakeholders to define business needs and provide \textbf{analytical support} for strategic and operational initiatives.}
\resumeItem{\textbf{Key Achievements}: 
\vspace{-4pt}
    \begin{itemize}
        \item Utilized \textbf{simulation models} to reduce the spread of infectious diseases across travel networks in Pacific Island countries, leading to improved \textbf{epidemic control strategies}.
        \item Presented research findings at the \textbf{\textit{7th Southern Cross Australasian Travel and Tropical Medicine Conference}}, contributing valuable insights to the field of infectious disease control in Pacific Island nations.
    \end{itemize}
}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}



%-----------PROJECTS-----------
\section{Projects}

\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Sales Data Copilot: Lakehouse Pipeline with GenAI | Team Leader}}{\href{https://github.com/DataCody/Sales-Copilot-Lakehouse}{\underline{Link}}}
\vspace{-13pt}
\resumeItemListStart
  \resumeItem{Developed an end-to-end \textbf{AI-powered Lakehouse platform} (“Sales Copilot”), enabling \textbf{retail analytics from ingestion to insight}—integrating data ingestion pipelines, smart data modeling, and Copilot-driven insights.}
  \resumeItem{Engineered data workflows using Python with scalable lakehouse design, supporting structured/unstructured datasets—for intelligent KPI generation and automated sales reporting.}
  \resumeItem{Implemented Copilot features for \textbf{retail decision support}, enabling semantic querying and on-demand insight generation for sales teams.}
  \resumeItem{Leveraged technologies such as \textbf{Lakehouse architecture}, \textbf{AI Copilot}, and \textbf{smart analytics}, demonstrating full-stack data engineering and AI integration.}
\resumeItemListEnd


\vspace{-18pt}
\resumeProjectHeading{\textbf{Energy Storage Value Optimization in PV Systems | Team Leader}}{\href{https://github.com/DataCody/Photovoltaic-Grid-Analysis}{\underline{Link}}}
\resumeItemListStart
  \resumeItem{Developed an interactive \textbf{Power BI} dashboard to evaluate photovoltaic system performance, electricity market trends, and battery storage ROI across multiple regions.}
  \resumeItem{Processed and integrated \textbf{hourly solar generation data} from Australia, Brazil, India, and Norway (2024), covering DC/AC output, irradiance, module/ambient temperature, and energy yields.}
  \resumeItem{Enriched analysis with \textbf{electricity price, demand, and supply data} via the OpenNEM REST API for Australia, enabling real-world revenue estimation and market feasibility studies.}
  \resumeItem{Calculated key KPIs including inverter efficiency, cumulative yields, system performance ratio, and estimated annual revenue of \textbf{AUD 7.97K} with a payback period of 4 years.}
  \resumeItem{Applied time-series analysis to identify performance patterns, temperature-efficiency correlations, and optimal battery dispatch strategies for increased profitability.}
\resumeItemListEnd
\vspace{-10pt}

\resumeSubHeadingListEnd

%-----------PUBLICATION-----------
\section{Publication}
\resumeSubHeadingListStart
\resumeSubheading
{Travel network analysis for infectious disease transmission in Pacific Island countries}{\href{https://sctravelmedconference.com/2024-program/}{\underline{Link}}}{7th Southern Cross Australasian Travel and Tropical Medicine Conference(Pg.10)}{Sep 2024}
\resumeSubHeadingListEnd


%-----------Certification-----------
\section{Certification}
\resumeSubHeadingListStart

\resumeSubheading
{Databricks Fundamentals}
{\href{https://credentials.databricks.com/722598a3-36f4-48a7-bd0a-371b86728229}{\underline{Credential}}}{DataBricks}{Mar - 2025}

\resumeSubheading
{dbt Fundamentals}{\href{https://www.linkedin.com/learning/certificates/dec770eacf4a3e72dddc0213d1a084d61513d60f754cd70ee35983675c492c8e?trk=share_certificate}{\underline{Credential}}}{Linkedin}{Feb - 2025}

\resumeSubheading
{Atlassian Agile Project Management Professional Certificate}{\href{https://www.linkedin.com/learning/certificates/39eb50dd7f9752c396a71d7f7df5da41666e1193da40bf45fe708b42c180d543}{\underline{Credential}}}{Atlassian}{Mar - 2025}

\resumeSubHeadingListEnd
\vspace{-18pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Master of Data Science}{}{The University of Queensland}{2022 - 2024}
\resumeSubHeadingListEnd
Completed data-driven research on travel networks \& infectious diseases.


% \resumeSubHeadingListStart
% \resumeSubheading
% {Hebei University}{2012 - 2016}{Bachelor of Tourism Management}{8.5/10 GPA}
% \resumeSubHeadingListEnd
% \vspace{-13pt}
%

%-----------REFERENCE-----------
\section{Reference}
\resumeSubHeadingListStart
\resumeSubheading
{Reference as request}{}{}{}
\resumeSubHeadingListEnd
\vspace{-5pt}

\end{document}
